Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-04-11 manuscript/manuscript.Rmd
Updated united tests to identify classed warnings.

  TODO: 
  - Add set_lambda, get_lambda, set_shift, get_shift methods.
  - implement into familiar
  - update familiar.experiment to allow for setting external configurations (or maybe make that the default -- its definitely easier and more transparent.)

>>>>

  TODO: 
  - implement into familiar
  - update familiar.experiment to allow for setting external configurations (or maybe make that the default -- its definitely easier and more transparent.)
